### 2022-06-13 manuscript.tex
Merge pull request #237 from SORTEE-Github-Hackathon/colebrookson-update-figure-caption [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2490456733

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ea3d52568405d25c555daffaef4bbf5a40954c92/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ea3d52568405d25c555daffaef4bbf5a40954c92}{SORTEE-Github-Hackathon/manuscript@ea3d525}
on June 10, 2022.

@@

\begin{figure}
\hypertarget{fig:github-diagram}{%
\centering
\includegraphics{images/github_diagram.png}
\caption{An overview of git's core features. A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place. B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project. C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities. D) CONTRIBUTING.md, LICENCE.md, \& README.md files can allow new team members or others wanting to use materials to understand the project components and learn how they can engage with the project and existing team members.}\label{fig:github-diagram}
}
\end{figure}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73}{SORTEE-Github-Hackathon/manuscript@3b6215a}
on June 13, 2022.

@@

\begin{figure}
\hypertarget{fig:github-diagram}{%
\centering
\includegraphics{images/github_diagram.png}
\caption{An overview of git's core features. A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place. \texttt{CONTRIBUTING.md}, \texttt{LICENCE.md}, and \texttt{README.md} files allow new team members, or others wanting to use materials, to understand the project components and learn how they can engage with the project and existing team members. B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project. C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities}\label{fig:github-diagram}
}
\end{figure}
